My title

### 2024-11-27 paper/paper.qmd
fixed launch issue with paper.qmd

In this 0-5 rating system, a score of 4 or above is often seen as the benchmark for a "highly rated" book. This is influenced by central tendency bias, where people naturally gravitate towards a moderate score, avoiding extremes like 0 or 5 to appear more balanced and objective. A rating such as 4, in particular, suggests a strong endorsement without overstepping into exaggeration. Given this, a critical question arises; What factors of a book contribute to the likelihood of the book being "highly rated"?

In this paper, I analyzed how the characteristics of a book, such as book type, page count, publishing year, and rating counts affected the likelihood of a book being "highly-rated", using the Children's Book Ratings Data (CITATION). First, after data cleaning, I selected 9 variables on children book characteristics for my analysis in (SECTION 2). Then, a logistic regression model was created to predict the probability of the book being "highly-rated", based on the chosen book characteristic variables.

The logistic regression model showed that ___ The findings of this research have practical implications for the writing industry, to allow future generation authors to push the boundaries of literature.

@@

```{r}
#| label: cleaned_dataset-preview
#| fig-cap: "Preview of the Cleaned Dataset"
#| echo: false

# TABLE 1: CLEANED DATASET
data %>% head(5)

data
```

@@

\newpage
```{r}
#| label: summary_statistic_cleaned_dataset3
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

model_file <- readRDS(file = here::here("models/model.rds"))

modelsummary(
  list (
    "Book is High-Rated" = model_file
  ),
  statistic = "mad"
)

@@

@@

@@

```
# References

>>>>

In this 0-5 rating system, a score of 4 or above is often seen as the benchmark for a "highly rated" book. This is influenced by central tendency bias, where people naturally gravitate towards a moderate score, avoiding extremes like 0 or 5 to appear more balanced and objective. A rating such as 4, in particular, suggests a strong endorsement without overstepping into exaggeration. Given this, a critical question arises; What factors of a book contribute to the likelihood of the book being "highly-rated" (a score above 4)?

In this paper, I analyzed how the characteristics of a book, such as book type, page count, publishing year, and rating counts affected the likelihood of a book being "highly-rated" using the Children's Book Ratings Data (CITATION). First, after data cleaning, I selected 9 variables on children book characteristics for my analysis in (SECTION 2). Then, a logistic regression model was created to predict the probability of the book being "highly-rated", based on the chosen book characteristic variables.

The logistic regression model showed that ___ .The findings of this research have practical implications for the writing industry, to allow future generation authors to push the boundaries of literature.

@@

```{r}
#| label: cleaned_dataset-preview
#| fig-cap: "Preview of the Cleaned Dataset"
#| message: false
#| echo: false
#| warning: false

# TABLE 1: CLEANED DATASET
data %>% 
  head(5) %>%
  kable(booktabs = TRUE, linesep = "") %>%
  kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)

@@

\newpage

@@

# delete this later
model_file <- readRDS(file = here::here("models/model.rds"))

@@

analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))

@@

-->
# References
